Template for indicator documentation

### 2023-09-08 trophic_levels-biomass_indicators.rmd

ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
   geom_spatraster(data=forest_diffherb)+
   ggtitle("Difference in forest herbivores from expectation")+
   scale_fill_distiller(type="div",palette='RdYlBu',limit=c(-100,100),oob=squish,na.value=NA, "% difference from \nexpected biomass")+
   facet_wrap(~lyr)+theme_bw()

@@

ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
   geom_spatraster(data=forest_diffcarn)+
   ggtitle("Difference from expected carnivore biomass")+
   scale_fill_distiller(type="div",palette='RdYlBu',limit=c(-100,100),oob=squish,na.value=NA,"% difference from\nexpected biomass")+
   facet_wrap(~lyr)+theme_bw()

>>>>

ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
   geom_spatraster(data=forest_diffherb)+
   ggtitle("Difference in forest herbivores from expectation")+
   scale_fill_distiller(type="div",palette='RdYlBu',limit=c(-100,100),oob=squish,na.value=NA, "% difference from \nexpected biomass")+
   facet_wrap(~lyr)+theme_bw()+
  labs(x="Year", y="Difference")

@@

ggplot()+geom_sf(data=norcounty,fill="white",lwd=0.1)+
   geom_spatraster(data=forest_diffcarn)+
   ggtitle("Difference from expected carnivore biomass")+
   scale_fill_distiller(type="div",palette='RdYlBu',limit=c(-100,100),oob=squish,na.value=NA,"% difference from\nexpected biomass")+
   facet_wrap(~lyr)+theme_bw()+
  labs(x="Year", y="Difference")
